Using VDMS to Search 100M Images: A Piece of Cake

### 2020-01-15 yfcc100m/paper/vldb2020/design.tex
Add more figures and other minor additions

@@

% \textbf{Client Library:}
% A user application can use the VDMS API by defining metadata conforming to the
% query protocol we have defined and passing along blobs. The client side VDMS
% library provides a simple query function that accepts a JSON string with
% commands and an array or vector of blobs.
% Internally, the library wraps the query string and blob using Google Protobufs
% and sends it to VDMS. It also receives a similarly wrapped response from VDMS
% and returns it to the client. The responses require JSON parsing on the client
% side for the metadata string that indicates how to interpret blobs.
% VDMS provides Python and C++ client libraries with mainly
% one function: a query that passes metadata as a JSON string and,
% optionally, data as a vector of blobs. The VDMS client library manages the
% rest.

>>>>

\begin{figure}[]
\centering
\includegraphics[width=1\columnwidth]{figures/vdms_arch.pdf}
\caption{VDMS Architecture}
\label{fig:arch}
\end{figure}

@@

\textbf{Client Library:}
A user application can use the VDMS API by defining metadata conforming to the
query protocol we have defined and passing along blobs. The client side VDMS
library provides a simple query function that accepts a JSON string with
commands and an array or vector of blobs.
Internally, the library wraps the query string and blob using Google Protobufs
and sends it to VDMS. It also receives a similarly wrapped response from VDMS
and returns it to the client. The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret blobs.
VDMS provides Python and C++ client libraries with mainly
one function: a query that passes metadata as a JSON string and,
optionally, data as a vector of blobs. The VDMS client library manages the
rest.
